BioTime

### 2019-04-16 biotime.Rmd
Join biotime and trait data.

bird_trait_data <- bird_ids  %>%
  select(acceptedNameUsageID, input) %>%
  distinct() %>%
  right_join(bird_trait, by = c("input" = "scientific")) %>%
  rename(scientific = input)
```

@@

Are there any studies for which we have trait data for all species?
```{r}
bird_data <- biotime_data %>%
  filter(taxa == "Birds") %>%
  left_join(bird_ids)
```

>>>>

bird_trait_data <- bird_ids  %>%
  select(id = acceptedNameUsageID, input) %>%
  distinct() %>%
  right_join(bird_trait, by = c("input" = "scientific")) %>%
  rename(scientific = input)
```

@@

Are there any studies for which we have trait data for all species?
```{r}
bird_data <- biotime_data %>%
  filter(taxa == "Birds") %>%
  left_join(bird_trait_data) 
```
